\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-10-03 gwnnDraft02.tex

\begin{table*}[t]
\begin{center}
\begin{tabular}{ |p{2cm}||p{3cm}|p{3cm}|p{3cm}|p{2cm}|  }
 \hline
 \multicolumn{5}{|c|}{Parameters for multi-hidden sector benchmarks} \\
 \hline
\multicolumn{5}{|c|}{Maximized signal} \\
 \hline
 Sector & Higgs vev (GeV) & $\Lambda^{AS}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & Index\\
 \hline
 1 & $24.6 \times 10^{9}$ & 38.6 & 87.7 & $10^{16}$ \\
 \hline
\multicolumn{5}{|c|}{Large split} \\
 \hline
 Sector & Higgs vev (GeV & $\Lambda^{AS}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & Index\\
 \hline
 1 & $246 \times 10^6$  & 10.8 & 30.3 & $10^{12}$ \\
 2 & $7.8 \times 10^9$  & 28.1 & 78.6 & $10^{15}$ \\
 \hline
 \multicolumn{5}{|c|}{Medium split} \\
 \hline
 Sector & Higgs vev (GeV) & $\Lambda^{AS}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & Index\\
 \hline
 1 & $246 \times 10^{6}$ & 10.8 & 30.3 & $10^{12}$ \\
 2 & $778 \times 10^6$  & 14.9 & 41.6 & $10^{13}$ \\
 \hline
 \multicolumn{5}{|c|}{Five sectors} \\
 \hline
 Sector & Higgs vev (GeV) & $\Lambda^{AS}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & Index\\
 \hline
 1 & $246 \times 10^6$ & 10.8 & 38.8 & $10^{12}$ \\
 2 & $426 \times 10^6$ & 12.6 & 45.2 & $3*10^{12}$ \\
 3 & $778 \times 10^6$ & 14.9 & 53.3 & $10^{13}$ \\
 4 & $1.3 \times 10^9$ & 17.3 & 62.1 & $3*10^{13}$ \\
 5 & $2.5 \times 10^9$ & 20.5 & 73.3 & $10^{14}$ \\
 \hline
\end{tabular}
\caption{Outline of parameters used for the various multi-hidden sector scenarios. The higgs vev is the vev for the given additional sector, $\Lambda^{AS}_{QCD}$ is the QCD phase transition in the additional sector, and $T_\gamma$ is the temperature of the SM photon bath when the SFOPT occurs in the additional sector. The index indicates the equivalent sector from the $N$naturalness model (Eq.~(\ref{eqn:vevs})).}\label{tab:cases}
\end{center}
\end{table*}

@@

In this work, it is assumed that $\delta t = 14$ days, but this may underestimate the capabilities of SKA as well as the cadences of the pulsar populations. If the timing residuals are lowered the maximum frequency reach of SKA increases, and the corresponding PSI curves in Figs.~(\ref{fig::Nnatural}) $\&$ ~(\ref{fig:Haa}) are shifted to the right, possibly giving the PTAs sensitivity to some of the scenarios considered here.

>>>>

\begin{table*}[t]
\begin{center}
\begin{tabular}{ |p{2cm}||p{3cm}|p{3cm}|p{3cm}|p{2cm}|  }
 \hline
 \multicolumn{5}{|c|}{Parameters for multi-hidden sector benchmarks} \\
 \hline
\multicolumn{5}{|c|}{Maximized signal} \\
 \hline
 Sector & Higgs vev (GeV) & $\Lambda^{AS}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & Index\\
 \hline
 1 & $24.6 \times 10^{9}$ & 38.6 & 87.7 & $10^{16}$ \\
 \hline
\multicolumn{5}{|c|}{Large split} \\
 \hline
 Sector & Higgs vev (GeV & $\Lambda^{AS}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & Index\\
 \hline
 1 & $246 \times 10^6$  & 10.8 & 30.3 & $10^{12}$ \\
 2 & $7.8 \times 10^9$  & 28.1 & 78.6 & $10^{15}$ \\
 \hline
 \multicolumn{5}{|c|}{Medium split} \\
 \hline
 Sector & Higgs vev (GeV) & $\Lambda^{AS}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & Index\\
 \hline
 1 & $246 \times 10^{6}$ & 10.8 & 30.3 & $10^{12}$ \\
 2 & $778 \times 10^6$  & 14.9 & 41.6 & $10^{13}$ \\
 \hline
 \multicolumn{5}{|c|}{Five sector} \\
 \hline
 Sector & Higgs vev (GeV) & $\Lambda^{AS}_{QCD}$ (GeV) & $T_\gamma$ (GeV) & Index\\
 \hline
 1 & $246 \times 10^6$ & 10.8 & 38.8 & $10^{12}$ \\
 2 & $426 \times 10^6$ & 12.6 & 45.2 & $3\times10^{12}$ \\
 3 & $778 \times 10^6$ & 14.9 & 53.3 & $10^{13}$ \\
 4 & $1.3 \times 10^9$ & 17.3 & 62.1 & $3\times10^{13}$ \\
 5 & $2.5 \times 10^9$ & 20.5 & 73.3 & $10^{14}$ \\
 \hline
\end{tabular}
\caption{Outline of parameters used for the various multi-hidden sector scenarios. The higgs vev is the vev for the given additional sector, $\Lambda^{AS}_{QCD}$ is the QCD phase transition in the additional sector, and $T_\gamma$ is the temperature of the SM photon bath when the SFOPT occurs in the additional sector. The index indicates the equivalent sector from the $N$naturalness model (Eq.~(\ref{eqn:vevs})).}\label{tab:cases}
\end{center}
\end{table*}

@@

In this work, it is assumed that $\delta t = 14$ days, but this may underestimate the capabilities of SKA as well as the cadences of the pulsar populations. If the timing residuals are lowered the maximum frequency reach of SKA increases, and the corresponding PSI curves in Figs.~\ref{fig::Nnatural} $\&$ \ref{fig:Haa} are shifted to the right, possibly giving the PTAs sensitivity to some of the scenarios considered here.
